\title{
02257 Applied functional programming \\
Project 1 \\
Interpreter for an imperative programming language
}
\author{
        Karol Dzitkowski - s142246
}
\date{\today}

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\begin{document}
\maketitle
\setlength{\parindent}{0pt}
With the signatures the group membersaccount for:
\begin{enumerate}
\item The extension from the minimal solution is made by the group
members only
\item No part of their solution is distributed to other groups
\item The group members have contributed equally to the solution
\end{enumerate}
Group members:
\begin{itemize}
\item Karol Dzitkowski - s142246
\end{itemize}
Signatures:
\clearpage

\section{Status of the solution}
I managed to successfully implement interpreter for all predefined $.while$ files. 
I wrote two additional scripts: Example1.while and Example2.while which are also working properly.
These examples are testing features of the language like nested procedures, returning values, 
code multiline, nested comments and even passing constant values to the procedure. 
All of these seems to work.

\section{Extensions}
Due to I worked alone I added only support for writing multiline and possibly nested comments in a code,
and also a functionality of passing parameters as constants (which won't be changed by a procedure) till
it was anoying when one had to use temporary variables since all parameters are passed by references. It
is done by using a new keyword $const$ and is different than passing parameter by value (using $!$). The
value is locally copied and stored in store with different location and procedure is working on a copied value.

\section{Reflections}
I found writing a simple interpreter in $F\#$ relatively easy and prowerful. What is still most annoying
right now is lack of simple operators $+,-,...$ which can be used in normal way instead of using them like
a normal functions. It was also really easy to debug parsing which I found really convenient. In every
programming language comments are essential for writing a good readable code so I decided to add this
feature as it was really easy using fslex even for a nested comments when we have to follow the scope of
comments. Summing up I think $F\#$ is an amazing tool for writing interpreters for all kind of languages.

\end{document}